Compositional Certified Resource Bounds\ifshort{\vspace{-.15cm}}{}

### 2014-11-07 paper/main.tex
experiments, they look ridiculous

>>>>

\begin{table}[t]
\centering
\begin{tabular}{r|c|c|c}
Function & LoC & Bound & Time (s) \\
\hline
\code{adpcm\_coder} & 145 & $1+|[0,\code{N}]|$ & 0.6 \\
\code{adpcm\_decod} & 130 & $1+|[0,\code{N}]|$ & 0.2 \\
\code{BF\_cfb64\_enc} & 151 & $1+2|[-1,\code{N}]|$ & 0.7 \\
\code{BF\_cbc\_enc} & 180 & $2+0.25|[-8,\code{N}]|$ & 1.0 \\
\code{mad\_bit\_crc} & 145 & $61.19{+}0.19|[-1,\code{N}]|$ & 0.4 \\
\code{mad\_bit\_read} & 65 & $1+0.12|[0,\code{N}]|$ & 0.05 \\
\code{MD5Update} & 200 & $133.95{+}1.05|[0,\code{N}]|$ & 1.0 \\
\code{sha\_update} & 98 & $2 + 3.55|[0,\code{N}]|$ & 1.2 \\
\end{tabular}
\vspace{.1cm}
\caption{Evaluation of our automatic amortized analysis on larger
C code from the cBench benchmark suite. The function analyzed might
be calling helper functions which do not appear in the list but have
to be analyzed.  These functions are accounted for in the LoC column
where not only the lines count of the analyzed function is called
but also the line count of all the funtions it calls. The line count
is computed on pre-processed C with all unnecessary declarations
removed.}
\label{tab:compar}
\end{table}
